---
output: github_document
---

```{r, include = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
library(fs)
library(here)
library(glue)
library(gt)

```


# Whats all this then?

It's my repository for #tidytuesday entries!  I'll include code and submission week by week.

# What's #TidyTuesday?

Either you have an interest in cleaning house on Tuesday or you like #rstats, #tidyverse &#R4DS!

TidyTuesday is an initative grown out of Jesse Mostipak (@kierisi) #R4DS & the community mentor group, started by Thomas Mock (@thomas_mock).  You can read all about it and get involved [here](https://github.com/rfordatascience/tidytuesday/blob/master/README.md)

```{r, echo = FALSE, include = FALSE, eval = FALSE}
image_table <- tibble(path = dir_ls(here(), glob = "*.png", recurse = 2)) %>% 
  mutate(file = basename(path),
         year = as.numeric(str_extract(path, "[0-9]{4}(?=\\/)")),
         week = as.numeric(str_extract(path, "(?<=week)\\d{1,2}"))) %>% 
  arrange(year, week, file, path) %>% 
  group_by(year, week) %>% 
  mutate(idx = row_number()) %>% 
  ungroup() %>% 
  mutate(tag = glue("tt_{year}_{week}{ifelse(length(idx) > 1, glue('_{idx}'), '')}.png")) %>% 
  mutate(path = as.character(path)) %>% 
  select(year, week, idx, path)
```

```{r, echo = FALSE, eval = FALSE}
image_table %>% 
  filter(year  == 2018) %>% 
  gt() %>%
  text_transform(
    locations = cells_body(columns = vars(path)),
    fn = function(x) {
      map(x, ~local_image(
        filename = .x,
        height = 100
      ))
    }
  ) %>% 
  tab_options(table.width = pct(100))
```